---
title: "A1 submission"
author: '22804897'
date: '2023'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminary steps

```{r init, include=FALSE}
library(tidyverse)
library(tree)
options(scipen=999)
```

### Data import, checking dimensions and data types, and setting the seed for sampling
```{r import data}
main_data <- read.csv('A1_data.csv', header=TRUE, stringsAsFactors = TRUE)
dim(main_data)
str(main_data)
set.seed(7)
```

### Sampling the data, sorting by Identifier and extracting the 1^st^, 10^th^, 20^th^ and 100^th^ Identifier values
```{r sample data}
test_data <- sample_n(main_data, 2500, replace = FALSE)
test_data <- test_data[order(test_data$Identifier, decreasing = FALSE),]

test_data[1,]$Identifier
test_data[10,]$Identifier
test_data[20,]$Identifier
test_data[100,]$Identifier
```

## Question 1

```{r question 1}
mean(test_data$Price)
```

## Question 2

```{r question 2}
boxplot(test_data$Price, main = "Price distribution", xlab = "Price", col = "orange", border = "brown", horizontal = TRUE)

quartiles <- quantile(test_data$Price)
quartiles

minPrice <- quartiles[1]
maxPrice <- quartiles[5]
Range <- maxPrice - minPrice

quartile1 <- quartiles[2]
names(quartile1) <- NULL
quartile1

quartile3 <- quartiles[4]
names(quartile3) <- NULL
quartile3

IQR <- quartile3 - quartile1
```
The price distribution of the properties has a wide range from the lowest price being `r minPrice` to the largest being `r maxPrice`, i.e. the Range is `r Range`. However, most of the properties prices range between `r quartile1` and `r quartile3`, with the Interquartile Range being `r IQR`.

## Question 3

```{r question 3}
ggplot(data = test_data, aes(x = test_data$Type)) + geom_bar() + labs(title = "Number of each type of property", x = "Type", y = "Amount of properties") + theme(plot.title = element_text(hjust = 0.5))
```

## Question 4

```{r question 4}

```

